---
title: "Looking for Solutions to a Regional Crisis"
author: "MA615 2021"
date: "10/5/2021"
output: ioslides_presentation
---

```{r setup, include=FALSE}
library(knitr)
library(png)
library(jpeg)
library(grid)
library(gridExtra)
library(tidyverse)
library(readxl)
```

## Trouble in the Sahel

<div style="font-size: 14pt">
The the Sahel in Africa is the region between the Sahara Desert and the Savanah. 
It includes the countries Burkina Faso, Cameroon, Chad, The Gambia, Guinea Mauritania, Mali, Niger, Nigeria and Senegal.
</div>

```{r fig.height=4,echo=FALSE, warning=FALSE}


img <- readJPEG("Sahel.jpg")
 grid.raster(img)
 
```


-----

<div style="font-size: 14pt">
The UN has described the Sahel as a
[land of opportunities](https://www.un.org/africarenewal/sahel), but today it is in crisis.  Violence in the Mali and Burkina Faso has created a refugee crisis.
[UN Refugee Agency site for Sahel crisis](https://data2.unhcr.org/en/situations/sahelcrisis)
</div>

```{r fig.height=4,echo=FALSE, warning=FALSE}
img <- readJPEG("camp.jpg")
 grid.raster(img)
 
```

-----


```{r fig.height=4,echo=FALSE, warning=FALSE}
img <- readPNG("refugee.png")
 grid.raster(img)
 
```





## The Question and the Data

<div style="font-size: 14pt">
What are the economic factors that affect this troubled region?  Do they offer any hope for quelling the suffering and violence?


One source of information is the World Bank which tracks both poverty and spending power ( a measure of prosperity).


Poverty -- see [Multidimensional Poverty Measure (MPM)](https://datacatalog.worldbank.org/search/dataset/0037589/World-Bank-s-Multidimensional-Poverty-Measure)

Spending power -- see [International Comparison Program (ICP)](https://www.worldbank.org/en/programs/icp).  

</div>




## Areas of relative prosperity

```{r fig.height=4,echo=FALSE, warning=FALSE}

img <- readPNG("ppp.png")
 grid.raster(img)
 
```
<div style="font-size: 14pt">
PPP is an economic theory that compares different contries' currencies through a "basket of goods" approach.
</div>


-----

```{r fig.height=4,echo=FALSE, warning=FALSE}

img <- readPNG("monetary.png")
 grid.raster(img)
 
```





## Extreme Poverty 

```{r fig.height=4,echo=FALSE, warning=FALSE}

img <- readPNG("food.png")
 grid.raster(img)
 
```


-----

```{r fig.height=4,echo=FALSE, warning=FALSE}

img <- readPNG("povcorr.png")
 grid.raster(img)
 
```



## data sources 

Spending power data is available by country here: [Data Bank ICP 2017](https://databank.worldbank.org/source/icp-2017).

World Bank Poverty data is available here:
 [Multidimensional Poverty Measure](https://www.worldbank.org/en/topic/poverty/brief/multidimensional-poverty-measure)

